Binocular integration of chromatic and luminance signals

### 2024-04-02 manuscript.tex
Minor edits to text

A useful framework for understanding binocular signal processing is the
two-stage gain control model of binocular combination introduced by
Meese et al. (2006). This model features interocular suppression between
monocular channels, followed by binocular summation. The model accounts
well for the pattern of contrast discrimination (`dipper') functions for
four distinct ocular configurations (see also Georgeson et al., 2016),
illustrated in Figure~\ref{fig-exampledips}. In the monocular condition,
participants must discriminate between stimuli of two contrasts (a
`pedestal', and a `pedestal plus target') that are both presented to one
eye, whilst the other eye views mean luminance. Threshold is defined as
the minimum target contrast required to make this judgement with 75\%
accuracy. The binocular condition is the same, except that the same
stimuli are shown to both eyes. In the half-binocular condition the
pedestal is shown to both eyes, but the target increment shown only to
one eye. Finally, the dichoptic condition involves presenting the
pedestal to one eye, and the target increment to the other eye.

@@

A further property of `blob' regions is that they are less strongly
orientation-tuned than other regions of V1 (Horton \& Hubel, 1981;
Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
(Edwards et al., 1995; Tootell et al., 1988). Our recent work has
investigated binocular combination for flickering discs of luminance,
which are DC-balanced across time (Segala et al., 2023). Steady-state
EEG responses from early visual cortex and psychophysical contrast
matching data were both consistent with weak interocular suppression
when using this stimulus arrangement. This is very different from the
`ocularity invariance' that is well-established when using DC-balanced
periodic stimuli such as sine-wave gratings, and implies strong
interocular suppression (Baker \& Wade, 2017; Meese et al., 2006; Moradi
\& Heeger, 2009). There is additional psychophysical evidence from
matching studies that binocular combination can be close to linear for
luminance increments (Anstis \& Ho, 1998; Levelt, 1965), particularly
against a dark background (Baker et al., 2012). Both structural and
functional data therefore imply that binocular combination may differ
between spatial and temporal contrast.

@@

Psychometric functions from each experiment were fit using
\emph{psignifit} 4 to estimate threshold and slope parameters via a
Bayesian numerical integration method (Schütt et al., 2016). A
cumulative Gaussian was used as the underlying function, and we
converted the slope estimates (\(\sigma\) parameters from the fitted
Gaussians) to equivalent Weibull \(\beta\) values using the
approximation \(\beta = 10.3/\sigma\).

@@

where \(C_L\) and \(C_R\) are the contrasts displayed to the left and
right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are
free parameters in the model. A further free parameter, \(k\),
represents additive internal noise, and is used to convert the model
outputs to either d-prime or threshold values (note that in the original
model specification (Meese et al., 2006) this parameter was called
\(\sigma\), but we use the \(k\) symbol here to avoid confusion with the
standard deviation of the cumulative Gaussian used when fitting the
psychometric functions to derive thresholds). Thresholds are defined by
iteratively adjusting the target contrast until the following equality
is satisfied:

@@

We ran the simplex algorithm from 100 random starting vectors for each
data set, and chose the solution for each data set that gave the
smallest RMS error.

@@

\caption{\label{fig-dipperfig}Dipper functions and psychometric slopes
from Experiment 1, averaged across three participants. Panels (a-c) show
threshold data, and panels (d-f) represent the slope of the psychometric
function expressed in Weibull \(\beta\) units. Error bars give ±1SE
across participants. Note that contrast values are expressed as a
percentage of the maximum displayable contrast (see Procedures for
details). Curves in panels (a-c) show the best fitting models, optimized
using a simplex algorithm (described in section 4.4), and RMSE values
give the root mean square errors of the fits.}

@@

Following Meese et al. (2006), we also inspected the slope of the
psychometric function for each condition (see
Figure~\ref{fig-dipperfig}d-f). At detection threshold, slopes were
relatively steep for all stimuli, with \(\beta\) values around 4. As
pedestal contrasts increased, slopes linearized and reduced to around
\(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained
shallow at high pedestal contrasts. The exception to this was the
dichoptic condition, where slopes became extremely steep at high
dichoptic mask contrasts, consistent with previous observations (Baker
et al., 2013; Meese et al., 2006). This was clear for all three data
sets, with slope values in the range \(4 < \beta < 8\). However, we
observe that slope estimates are more variable than threshold estimates
(note the large error bars), particularly when using adaptive
staircases, which deploy the majority of trials close to threshold. Our
second experiment therefore investigated the slope of the psychometric
function in more detail for dichoptic masking using the method of
constant stimuli.

@@

In our final experiment, we again measured dipper functions, but this
time for a temporally modulating luminance disc. This was motivated by
our recent work (Segala et al., 2023) that appeared to show increased
binocular facilitation and reduced interocular suppression for
flickering disc stimuli (relative to gratings), measured using EEG and a
psychophysical matching paradigm. The pattern of dipper functions for a
4Hz flickering disc (see Figure~\ref{fig-discdata}a) was very similar to
that observed for achromatic gratings (see Figure~\ref{fig-dipperfig}a),
and the binocular summation ratio at threshold was also similar (a
factor of 1.49 for discs, vs 1.67 for gratings). Threshold data for
individual participants are shown in Figure~\ref{fig-individualdiscs}.
We also found a similar pattern of psychometric slope values
(Figure~\ref{fig-discdata}b) as we had for gratings, though we note that
the dichoptic condition did not produce the `super-steep' psychometric
functions we had observed in Experiments 1 \& 2. Nevertheless, the
dichoptic slopes are somewhat above those of the other pedestal
arrangements at high contrasts.

@@

For consistency with previous work, we initially performed least-squares
fits of the two-stage model (Meese et al., 2006) for each of the
chromaticity experiments, and the flickering disc experiment (7 free
parameters per fit). The best model fits are shown by the curves in
Figure~\ref{fig-dipperfig} \& Figure~\ref{fig-discdata}, and provide an
excellent description of the data, with RMS errors between 1.06 and
1.59dB. Best fitting parameters are shown in the `Simplex fits' section
of Table~\ref{tbl-parametertable}. We note that in previous work, the
weight of interocular suppression (\(\omega\) in the model) is
implicitly fixed at 1. Here we allowed it to vary, but it still received
a value of exactly 1 in all of our grating conditions, and slightly
below 1 (0.89) for our flickering discs. The exponent values (\emph{p}
and \emph{q}) for the red/green gratings are rather different from those
of the other conditions. In previous work (Meese et al., 2006) the
second stage gain control nonlinearity (Equation 4) does typically have
quite substantial exponent values, which balance the relatively mild
nonlinearity at the first stage, and produce a compressive transducer
that results in contrast masking (the handle of the dipper). The high
value of \emph{p} = 19.42 is therefore likely to be compensating for the
low value of \emph{m} = 1.03 at stage one, but may well represent the
combination of several successive stages of nonlinearity, and perhaps
also other phenomena such as uncertainty (Pelli, 1985).

We additionally implemented a hierarchical Bayesian version of the model
in order to estimate full posterior parameter distributions. This model
was fit simultaneously to the full trial-by-trial data from all
participants who participated in a given experiment (i.e.~the model was
fitted separately to each of the four dipper data sets).
Figure~\ref{fig-bayesianmodel}a-d summarises the model behaviour, which
displays the same pattern of dipper functions as we found empirically.
Mean posterior parameter values are given in the lower rows of
Table~\ref{tbl-parametertable}. These correspond quite closely to the
parameters from the simplex fitting and the original Meese et al. (2006)
parameters (reproduced in the first row of the table for reference). The
panels in the right and upper margins of Figure~\ref{fig-bayesianmodel}
show posterior distributions for each model parameter. Note in
particular that the posterior distribution for the weight of interocular
suppression (\(\omega\), top right panel) overlaps 1 for each
experiment, consistent with the strong dichoptic masking observed in the
threshold data. We note that the distribution for \(\omega\) in the
flickering disc condition is somewhat lower than for the other three
data sets. However this difference is not meaningful according to
criteria such as comparing the 95\% credible intervals of the
distribution to a value of \(\omega=1\).

@@

Finally we fitted an extended model, that included interocular
suppression between the different pathways, to the data of Experiment 2.
Figure~\ref{fig-MCSmodel} shows the model curves (panels a-c), which
correspond closely to the data in Figure~\ref{fig-MCSfig}. One striking
discrepancy is that the model predicts a region of negative d-prime for
the case where the target and dichoptic mask have the same chromaticity
(see the curved regions below 50\% correct). This feature was not
generally present in our data, though it can be observed for one
participant in Figure~\ref{fig-individualMCS}b,c.~Our previous work
(Baker et al., 2013) has found evidence for this phenomenon (termed
`swan functions'), but it generally requires very high mask contrasts to
be measurable empirically, and there may also be some individual
differences; both factors might explain its absence here.

Figure~\ref{fig-MCSmodel}d,e shows the model estimates for the weight of
interocular suppression in each combination of target and mask
chromaticity. Although the weights might appear to indicate that
(excluding within-mechanism effects) suppression is strongest between
blue/yellow targets and achromatic masks (a weight of 0.56), this is
somewhat complicated by the differences in sensitivity and mask contrast
between conditions. We selected mask contrasts that were approximately
equal multiples (\(16\times\)) of their own detection thresholds, based
on the data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
modelling expressed these contrasts as a percentage of the maximum
contrast that it was possible to display on the monitor (see
Procedures). The values in brackets in Figure~\ref{fig-MCSmodel}d
indicate the overall suppressive term on the denominator, calculated by
multiplying the mask contrast by the fitted weight. These values
indicate that the strongest suppression is instead between red/green
targets and blue/yellow masks, consistent with the threshold elevation
observed empirically (Figure~\ref{fig-MCSfig}g). In principle it would
be possible to repeat this modelling using either cone contrast values,
or contrast expressed relative to detection threshold, which would
require re-fitting the model.

@@

Estimates of the binocular summation ratio at threshold fell within the
range \(\sqrt{2}\) to 2 for all four data sets. Consistent with previous
reports (Simmons, 2005), summation was slightly higher for chromatic
versus achromatic stimuli, but fell short of perfect linear summation (a
ratio of 2). In our model, summation at threshold is determined by the
exponent at the first gain control stage (the \emph{m} parameter in
Equations 1 \& 2). The summation ratio can be approximated by
\(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an exponent
of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\) produces
a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model fits (see
Table~\ref{tbl-parametertable}) generated parameter estimates in the
range \(1 < m < 1.4\), consistent with the high levels of summation
observed empirically.

@@

Previous work has demonstrated that the slope of the psychometric
function in 2AFC tasks can distinguish different types of masking,
although it is much less widely reported than threshold measures. In
particular, pedestal masking linearizes the slope (Foley \& Legge, 1981;
Meese et al., 2006), and within-channel dichoptic masking produces very
steep slopes (Baker et al., 2013; Meese et al., 2006). We replicate both
of these effects here, and show that they extend to isoluminant
chromatic pathways (see Figure~\ref{fig-dipperfig}d-f \&
Figure~\ref{fig-MCSfig}). We additionally show that dichoptic masking
between different pathways does not produce unusually steep slopes (see
Figure~\ref{fig-MCSfig}). It therefore more closely resembles other
types of masking between visual channels, such as cross-orientation
masking (Meese \& Baker, 2009), surround masking (Yu et al., 2002), and
masking from broadband noise (Baker \& Meese, 2012; Lu \& Dosher, 2008),
which also do not impact psychometric slopes.

@@

Recent evidence indicates that the physiological substrate of
interocular suppression may be neurons in layer 4 of primary visual
cortex (Dougherty et al., 2019). Most cells in this layer are
monocularly exciteable, in that their responses increase only by
stimulation of their preferred eye. However, simultaneous stimulation of
the non-preferred eye can modulate the response, usually in an
inhibitory fashion, exactly as proposed at stage 1 of the two-stage
model (Equations 1 \& 2). In terms of perception, one consequence of
this early suppression is to achieve `ocularity invariance', whereby the
perceived contrast of a stimulus viewed by one eye is equivalent to that
of the same stimulus viewed by both eyes (Baker et al., 2007). Similar
processes of invariance have also been reported using fMRI (Moradi \&
Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).

>>>>

A useful framework for understanding binocular signal processing is the
two-stage gain control model of binocular combination introduced by
Meese et al. (2006). This model features interocular suppression between
monocular channels, followed by binocular summation. The model accounts
well for the pattern of contrast discrimination (`dipper') functions for
four distinct ocular configurations (see also Georgeson et al., 2016),
illustrated in Figure~\ref{fig-exampledips}. In the monocular condition,
participants must discriminate between stimuli of two contrasts (a
`pedestal', and a `pedestal plus target') that are both presented to one
eye, whilst the other eye views mean luminance. Threshold is defined as
the minimum target contrast required to make this judgement with 75\%
accuracy. The binocular condition is the same, except that the stimuli
are shown to both eyes. In the half-binocular condition the pedestal is
shown to both eyes, but the target increment is shown only to one eye.
Finally, the dichoptic condition involves presenting the pedestal to one
eye, and the target increment to the other eye.

@@

A further property of `blob' regions is that they are less strongly
orientation-tuned than other regions of V1 (Horton \& Hubel, 1981;
Livingstone \& Hubel, 1984), and biased towards low spatial frequencies
(Edwards et al., 1995; Tootell et al., 1988). Our recent work has
investigated binocular combination for flickering discs of luminance,
which are DC-balanced across time (Segala et al., 2023). Steady-state
EEG responses from early visual cortex and psychophysical contrast
matching data were both consistent with weak interocular suppression
when using this stimulus arrangement. This is very different from the
`ocularity invariance' (where binocular and monocular stimuli appear
equal) that is well-established when using DC-balanced periodic stimuli
such as sine-wave gratings, and implies strong interocular suppression
(Baker \& Wade, 2017; Meese et al., 2006; Moradi \& Heeger, 2009). There
is additional psychophysical evidence from matching studies that
binocular combination can be close to linear for luminance increments
(Anstis \& Ho, 1998; Levelt, 1965), particularly against a dark
background (Baker et al., 2012). Both structural and functional data
therefore imply that binocular combination may differ between spatial
and temporal contrast.

@@

Psychometric functions from each experiment were fit using
\emph{psignifit} 4 to estimate threshold and slope parameters via a
Bayesian numerical integration method (Schütt et al., 2016). A
cumulative Gaussian was used as the underlying function, with contrast
values expressed in decibel (dB) units (where
\(C_{dB} = 20log_{10}(C_\%)\)). We converted the slope estimates
(\(\sigma\) parameters from the fitted Gaussians) to equivalent Weibull
\(\beta\) values using the approximation \(\beta = 10.3/\sigma\).
Threshold was defined as the target contrast corresponding to an
accuracy of 75\% correct.

@@

where \(C_L\) and \(C_R\) are the contrasts displayed to the left and
right eyes, and \(m\), \(S\), \(\omega\), \(p\), \(q\) and \(Z\) are
free parameters in the model. A further free parameter, \(k\),
represents additive internal noise, and is used to convert the model
outputs to either d-prime or threshold values (note that in the original
model specification (Meese et al., 2006) this parameter was called
\(\sigma\), but we use the \(k\) symbol here to avoid confusion with the
standard deviation of the cumulative Gaussian used when fitting the
psychometric functions to estimate thresholds). Thresholds are defined
by iteratively adjusting the target contrast until the following
equality is satisfied:

@@

We ran the simplex algorithm from 100 random starting vectors for each
data set, and chose the solution for each data set that gave the
smallest root mean squared error (RMSE) between the model and data.

@@

\caption{\label{fig-dipperfig}Dipper functions and psychometric slopes
from Experiment 1, averaged across three participants. Panels (a-c) show
threshold data, and panels (d-f) represent the slope of the psychometric
function expressed in Weibull \(\beta\) units. Error bars give ±1SE
across participants. Note that contrast values are expressed as a
percentage of the maximum displayable contrast (see Procedures for
details). Curves in panels (a-c) show the best fitting models, optimized
using a simplex algorithm, and RMSE values give the root mean squared
errors of the fits.}

@@

Following Meese et al. (2006), we also inspected the slope of the
psychometric function for each condition (see
Figure~\ref{fig-dipperfig}d-f). At detection threshold, slopes were
relatively steep for all stimuli, with values around \(\beta=4\). As
pedestal contrasts increased, slopes linearized and reduced to around
\(\beta=1.3\) (Foley \& Legge, 1981; Meese et al., 2006), and remained
shallow at high pedestal contrasts. The exception to this was the
dichoptic condition, where slopes became extremely steep at high
dichoptic mask contrasts, consistent with previous observations (Baker
et al., 2013; Meese et al., 2006). This was clear for all three data
sets, with slope values in the range \(4 < \beta < 8\). However, we
observe that slope estimates are more variable than threshold estimates
(note the large error bars), particularly when using adaptive
staircases, which deploy the majority of trials close to threshold. Our
second experiment therefore investigated the slope of the psychometric
function in more detail for dichoptic masking using the method of
constant stimuli, as well as exploring dichoptic interactions between
chromatic channels.

@@

In our final experiment, we again measured dipper functions, but this
time for a disc temporally modulating in luminance. This was motivated
by our recent work (Segala et al., 2023) that appeared to show increased
binocular facilitation and reduced interocular suppression for
flickering disc stimuli (relative to gratings), measured using EEG and a
psychophysical matching paradigm. The pattern of dipper functions for a
4Hz flickering disc (see Figure~\ref{fig-discdata}a) was very similar to
that observed for achromatic gratings (see Figure~\ref{fig-dipperfig}a),
and the binocular summation ratio at threshold was also similar (a
factor of 1.49 for discs, vs 1.67 for gratings). Threshold data for
individual participants are shown in Figure~\ref{fig-individualdiscs}.
We also found a similar pattern of psychometric slope values
(Figure~\ref{fig-discdata}b) as we had for gratings, though we note that
the dichoptic condition did not produce the `super-steep' psychometric
functions we had observed in Experiments 1 \& 2. Nevertheless, the
dichoptic slopes are somewhat above those of the other pedestal
arrangements at high contrasts.

@@

For consistency with previous work, we initially performed least-squares
fits of the two-stage model (Meese et al., 2006) for each of the
chromaticity experiments, and the flickering disc experiment (7 free
parameters per fit). The best model fits are shown by the curves in
Figure~\ref{fig-dipperfig} and Figure~\ref{fig-discdata}, and provide an
excellent description of the data, with RMS errors between 1.06 and
1.59dB. Best fitting parameters are shown in the `Simplex fits' section
of Table~\ref{tbl-parametertable}. We note that in previous work, the
weight of interocular suppression (\(\omega\) in the model) is
implicitly fixed at 1. Here we allowed it to vary, but it still received
a value of exactly 1 in all of our grating conditions, and slightly
below 1 (0.89) for our flickering discs. The exponent values (\emph{p}
and \emph{q}) for the red/green gratings are rather different from those
of the other conditions. In previous work (Meese et al., 2006) the
second stage gain control nonlinearity (Equation 4) does typically have
quite substantial exponent values, which balance the relatively mild
nonlinearity at the first stage, and produce a compressive transducer
that results in contrast masking (the handle of the dipper). The high
value of \emph{p} = 19.42 is therefore likely to be compensating for the
low value of \emph{m} = 1.03 at stage one, but may well represent the
combination of several successive stages of nonlinearity, and perhaps
also other phenomena such as uncertainty (Pelli, 1985).

We additionally implemented a hierarchical Bayesian version of the model
in order to estimate full posterior parameter distributions. This model
was fit simultaneously to the full trial-by-trial data from all
participants who participated in a given experiment (i.e.~the model was
fitted separately to each of the four dipper data sets).
Figure~\ref{fig-bayesianmodel}a-d summarises the model behaviour, which
displays the same pattern of dipper functions as we found empirically.
Mean posterior parameter values are given in the lower rows of
Table~\ref{tbl-parametertable}. These correspond quite closely to the
parameters from the simplex fitting and the original Meese et al. (2006)
parameters (reproduced in the first row of the table for reference). The
panels in the right and upper margins of Figure~\ref{fig-bayesianmodel}
show posterior distributions for each model parameter. Note in
particular that the posterior distribution for the weight of interocular
suppression (\(\omega\), top right panel) overlaps 1 for each
experiment, consistent with the strong dichoptic masking observed in the
threshold data. We note that the distribution for \(\omega\) in the
flickering disc condition is somewhat lower than for the other three
data sets. However this difference is not meaningful according to widely
accepted criteria such as comparing the 95\% intervals of the
distribution to a value of \(\omega=1\).

@@

Finally we fitted an extended model, that included interocular
suppression between the different pathways, to the data of Experiment 2.
Figure~\ref{fig-MCSmodel} shows the model curves (panels a-c), which
correspond closely to the data in Figure~\ref{fig-MCSfig}. One striking
discrepancy is that the model predicts a region of negative d-prime for
the case where the target and dichoptic mask have the same chromaticity
(see the curved regions below 50\% correct). This happens in the model
because low contrast targets suppress the mask more than they excite the
detecting mechanism, producing a net decrease in response. The feature
(termed a `swan function') was not generally present in our empirical
data, though it can be observed for one participant in
Figure~\ref{fig-individualMCS}b,c.~Our previous work (Baker et al.,
2013) has found evidence for this phenomenon, but it generally requires
very high mask contrasts to be measurable empirically, and there may
also be some individual differences; both factors might explain its
absence here.

Figure~\ref{fig-MCSmodel}d,e shows the model estimates for the weight of
interocular suppression in each combination of target and mask
chromaticity. Although the weights might appear to indicate that
(excluding within-mechanism effects) suppression is strongest between
blue/yellow targets and achromatic masks (a weight of 0.56), this is
somewhat complicated by the differences in mask contrast between
conditions. We selected mask contrasts that were approximately equal
multiples (\(16\times\)) of their own detection thresholds, based on the
data of Experiment 1 (Figure~\ref{fig-dipperfig}a-c). However the
modelling expressed these contrasts as a percentage of the maximum
contrast that it was possible to display on the monitor (see
Procedures). The values in brackets in Figure~\ref{fig-MCSmodel}d
indicate the overall suppressive term on the denominator of the model at
stage 1, calculated by multiplying the mask contrast by the fitted
weight. These values indicate that the strongest suppression is instead
between red/green targets and blue/yellow masks, consistent with the
threshold elevation observed empirically (Figure~\ref{fig-MCSfig}g). In
principle it would be possible to repeat this modelling using either
cone contrast values, or contrast expressed relative to detection
threshold, which would require re-fitting the model.

@@

Estimates of the binocular summation ratio at threshold fell within the
range \(\sqrt{2}\) to 2 for all four stimuli tested here. Consistent
with previous reports (Simmons, 2005), summation was slightly higher for
chromatic versus achromatic stimuli, but fell short of perfect linear
summation (a ratio of 2). In our model, summation at threshold is
determined by the exponent at the first gain control stage (the \emph{m}
parameter in Equations 1 \& 2). The summation ratio can be approximated
by \(2^{1/m}\) (see Figure 9 of Baker et al., 2012), such that an
exponent of \(m=1\) produces a ratio of 2, and an exponent of \(m = 2\)
produces a ratio of \(\sqrt{2}\). Both the simplex and Bayesian model
fits (see Table~\ref{tbl-parametertable}) generated parameter estimates
in the range \(1 < m < 1.4\), consistent with the high levels of
summation observed empirically.

@@

Previous work has demonstrated that the slope of the psychometric
function in 2AFC tasks can distinguish different types of masking,
although it is much less widely reported than threshold measures. In
particular, pedestal masking linearizes the slope (Foley \& Legge, 1981;
Meese et al., 2006), and within-channel dichoptic masking produces very
steep slopes (Baker et al., 2013; Meese et al., 2006). We replicate both
of these effects here, and show that they extend to the isoluminant
chromatic pathways (see Figure~\ref{fig-dipperfig}d-f \&
Figure~\ref{fig-MCSfig}). We additionally show that dichoptic masking
between different pathways does not produce unusually steep slopes (see
Figure~\ref{fig-MCSfig}). It therefore more closely resembles other
types of masking between visual channels, such as cross-orientation
masking (Meese \& Baker, 2009), surround masking (Yu et al., 2002), and
masking from broadband noise (Baker \& Meese, 2012; Lu \& Dosher, 2008),
which also do not impact psychometric slopes.

@@

Recent evidence indicates that the physiological substrate of
interocular suppression may be neurons in layer 4 of primary visual
cortex (Dougherty et al., 2019). Most cells in this layer are
monocularly exciteable, in that their responses increase only by
stimulation of their preferred eye. However, simultaneous stimulation of
the non-preferred eye can modulate the response, usually in an
inhibitory fashion, exactly as proposed at stage 1 of the two-stage
model (Equations 1 \& 2). In terms of perception, one consequence of
this early suppression is to achieve `ocularity invariance', whereby the
perceived contrast of a stimulus viewed by one eye is equivalent to that
of the same stimulus viewed by both eyes (Baker et al., 2007). Similar
processes of response invariance have also been reported using fMRI
(Moradi \& Heeger, 2009) and steady-state EEG (Baker \& Wade, 2017).
